\begin{abstract}
    With the increasing complexity of motorbike dashboard software, ensuring its reliability and functionality has become a significant challenge in the automotive industry. Traditional manual testing methods are labor-intensive, time-consuming and prone to human error. This study explores the application of deep learning-based object detection techniques to automate dashboard software validation.

    To implement the automated testing environment, the study proposes integrating a camera system with a hardware-in-the-loop setup. The hardware-in-the-loop system captures and processes dashboard images using a deep learning-based object detection algorithm, comparing detected elements to reference values for validation. This approach significantly enhances testing accuracy and repeatability.

    The research begins by analyzing traditional object detection techniques, including viola-jones, histogram of oriented gradients and deformable part-based models. Furthermore, the study highlights their limitations and explores the transition to deep learning-based object detection, it focuses on region-based convolutional neural networks, you only look once, and single shot multiBox detector. These models offer significant improvements in real-time detection, precision and robustness, making them ideal for automated dashboard validation.
    
    A key aspect of this study is the selection of an optimal camera system, as image quality directly impacts detection performance. Factors such as scanning method, resolution, dynamic range, sensor size, and frame rate are analyzed to determine their influence on object detection accuracy. The study finds that high resolution and high dynamic range capable cameras improve detection under challenging conditions, while area scan cameras are more suitable for real-time applications.
    
    
    The findings of this study demonstrate that deep learning-based object detection, combined with optimized camera selection and hardware-in-the-loop integration, presents a viable and scalable solution for dashboard software validation. Future research should focus on model training, dataset creation, and integration strategies.
    
    
\end{abstract}